% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Curriculum Vitae},
  pdfauthor={Zijin Zhang},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Curriculum Vitae}
\author{Zijin Zhang}
\date{}
\begin{document}
\maketitle


\begin{center}
    \textbf{\Large Zijin Zhang} \\ \vspace{5pt}
    % \seticon{faPhone} \ \small XXX-XXX-XXXX \quad
    Email: \href{mailto:zijin@ucla.edu}{zijin@ucla.edu} \quad
    Website: \href{https://beforerr.github.io/beforerr/docs/research/}{beforerr.github.io}
\end{center}

\section{Education}\label{education}

\begin{itemize}
\item
  Heliophysics Summer School, NASA's Living with a Star, UCAR/CPAESS, Boulder, Colorado, 2024
\item
  Graduate student in Planetary Science, \emph{University of California, Los Angeles}, 2022 - present
\item
  B.Sc. in Space Physics, \emph{University of Science and Technology of China}, 2018 - 2022
\end{itemize}

\section{Research Interests}\label{research-interests}

\begin{itemize}
\item
  Solar wind and wave‑particle interactions
\item
  Computational plasma physics and application of data science in space science
\item
  Solar physics, heliophysics and experimental space science
\end{itemize}

\section{Publications}\label{publications}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Zhang, Z.}, Artemyev, A., Mourenas, D., Angelopoulos, V., Zhang, X.-J., Kasahara, S., Miyoshi, Y., Matsuoka, A., Kasahara, Y., Mitani, T., Yokota, S., Hori, T., Keika, K., Takashima, T., Teramoto, M., Matsuda, S., \& Shinohara, I. (2024). Relativistic Electron Flux Decay and Recovery: Relative Roles of EMIC Waves, Chorus Waves, and Electron Injections. \emph{Journal of Geophysical Research: Space Physics}, 129(12), e2024JA033174. DOI: \href{https://doi.org/10.1029/2024JA033174}{10.1029/2024JA033174}
\item
  Margot, J.-L., Li, M. G., Pinchuk, \ldots{} \textbf{Zhang, Z.}. (2023). A search for technosignatures around 11680 stars with the green bank telescope at 1.15--1.73 GHz. \emph{Astronomical Journal}, 166(5), 206. DOI: \href{https://doi.org/10.3847/1538-3881/acfda4}{10.3847/1538-3881/acfda4}
\item
  \textbf{Zhang, Z.}, \& Tao, X. (2022). The kinetic simulation of the interaction between the Moon's magnetic anomalies and the solar wind. \emph{Undergraduate Thesis} {[}University of Science and Technology of China{]}. DOI: \href{http://dx.doi.org/10.13140/RG.2.2.15841.68968}{10.13140/RG.2.2.15841.68968}
\end{enumerate}

\section{Presentations}\label{presentations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Zhang, Z.}, Artemyev, A., Angelopoulos, V., \& Velli, M. (2024, December). On the Alfvénicity of multifluid force-free current sheet. \emph{American Geophysical Union}.
\item
  \textbf{Zhang, Z.}, Artemyev, A., Angelopoulos, V., \& Chen, S. (2023, December 14). Solar wind discontinuities spatial evolution and energetic ion scattering. \emph{American Geophysical Union}. DOI: \href{https://doi.org/10.13140/RG.2.2.12905.67682}{10.13140/RG.2.2.12905.67682}
\item
  \textbf{Zhang, Z.}, Artemyev, A., Mourenas, D., Angelopoulos, V., \& Zhang, X.-J. (2023, December 12). Relativistic electron flux decay and recovery: Relative roles of EMIC waves, whistler-mode waves, and plasmasheet injections. \emph{American Geophysical Union}. DOI: \href{https://doi.org/10.13140/RG.2.2.33038.33607}{10.13140/RG.2.2.33038.33607}
\item
  \textbf{Zhang, Z.}, Artemyev, A., Mourenas, D., Angelopoulos, V., \& Zhang, X.-J. (2023, June 22). Relativistic electron flux decay and recovery: Relative role of EMIC waves, whistler-mode waves, and plasmasheet injections. \emph{Geospace Environment Modeling}. DOI: \href{http://dx.doi.org/10.13140/RG.2.2.33038.33607}{10.13140/RG.2.2.33038.33607}
\end{enumerate}

\section{Software}\label{software}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Zhang, Z.} (2025). discontinuitypy: A python package for identifying and analyzing discontinuities for time series (Version v0.4.0) {[}Computer software{]}. Zenodo. DOI: \href{https://doi.org/10.5281/ZENODO.14868016}{10.5281/ZENODO.14868016}
\end{enumerate}

\section{Research Experience}\label{research-experience}

\begin{itemize}
\item
  Graduate Student Researcher, \emph{Experimental Space Physics Group}, 2022-present\\
  Study energetic ion scattering by solar wind discontinuities. 2022-present. \href{https://beforerr.github.io/ion_scattering_by_SWD}{Project website}.
\item
  Undergraduate Research Assistant, \emph{Artificial Intelligence of Things Lab}, 2021-2022\\
  Implemented a distributed system to monitor edge devices and automate IT deployment and management
\end{itemize}




\end{document}
